Edge sign prediction in general graphs and Correlation Clustering

### 2017-10-18 edge/conclusions.tex
add one ref

  \item Another rich class of graphs were predicting edge types would be a challenging and rewarding
    task is \textbf{multigraph}, which allow several edges between two nodes. It can also be seen as
    the flattening of several graphs sharing the same nodeset, but where the provenance of each edge
    would have been lost and need to be recover. With our original formulation of goodness as
    ${s_{uv}}^T w_{uv}$, only one direction can achieve the higher score (discarding the rare case
    of tie). One alternative we proposed was to let each $w_{uv}$ be a linear combination of a small
    number of base directions, although experimentally it did not fit well our synthetic data.
    Symmetrically, another idea could be to have more than one way to compute the similarity
    $s_{uv}$ between two nodes.

>>>>

  \item Another rich class of graphs were predicting edge types would be a challenging and rewarding
    task is \textbf{multigraph}, which allow several edges between two
    nodes~\autocite{typedMultigraph11}. It can also be seen as
    the flattening of several graphs sharing the same nodeset, but where the provenance of each edge
    would have been lost and need to be recover. With our original formulation of goodness as
    ${s_{uv}}^T w_{uv}$, only one direction can achieve the higher score (discarding the rare case
    of tie). One alternative we proposed was to let each $w_{uv}$ be a linear combination of a small
    number of base directions, although experimentally it did not fit well our synthetic data.
    Symmetrically, another idea could be to have more than one way to compute the similarity
    $s_{uv}$ between two nodes.
